CSci487 Penetration Testing Project: AILEE

### 2019-05-06 csci487/project/paper.tex
texttt appropriate commands
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>
Removed paragraphs about the new code that we're not using anymore :(
Signed-off-by: Grant Haataja <grant.haataja@gmail.com>

@@

Before beginning the development of the game, a suitable platform to run the environment needed to be found. The website Repl.it was decided upon, due to their extensive language support and the ability for multiple people to work simultaneously and have all changes automatically saved to the cloud. \cite{b1} The “Multiplayer” mode, as this feature was called, still had a lot of bugs, so forking the project and saving work manually was still necessary, but overall it made the development of AILEE much smoother.

@@

To enable smooth graphics for the intro screen and the game’s ending events, the Python Curses library was referenced and used extensively. \cite{b2} This provided the ability to control keyboard input while text displayed on the screen or the ending event graphics played, to increase the smoothness of gameplay.

@@

Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig. \ref{fig:access}).

@@

This is the code for the structure and mechanics of the computer filesystems. 
Similar to Linux, both files and folders have and use discrete permissions, 
marking certain files as readable, writable, and executable.  While there are not yet any
provisions for editing/creating files in-game\footnote{The \texttt{gcc} command
creates a file \texttt{a.out}, which promptly throws a segmentation fault.},
the permissions architecture is in place for adding future file-editing
utilities.

Executable files are created from a separate filesystem constructor.  Each
executable file simply is a \texttt{File} object with the executable bit set in
its permissions object, and the file contents are pure Python code that executes
when the file is run via the \texttt{run} command.  To verify that arbitrary
code is not run (which would break the game), executable files compare hashes
from creation to runtime to and will not run if the contents have been
altered.

@@

Directories are colored light blue, executables are light green, and regular files are white.  Because of the permissions associated with each file and directory, and the fact that \texttt{File} and \texttt{Directory} objects are implemented as separate classes, there are no special requirements to file/folder names or attributes.  However, due to the difficult implementation of a directory tree, the \textit{ls} command cannot be given a path argument as in real life, and thus can only be used in the current directory.

\section{Conclusion}
In summary, this project dives into many core concepts and facets of penetration testing, and simulates them to feel like the real-world counterparts. Many of the commands that simulate complicated software are coded creatively to look realistic even though they only work in the specific instances inside the game. AILEE is a demo, and there is much opportunity to expand the game into something far more complex and realistic if enough time and energy was dedicated to doing so.

\begin{thebibliography}{00}
\bibitem{b1} Repl.it, ``The world's leading online coding platform,'' repl.it. [Online]. Available: \url{https://repl.it/site/features}. [Accessed: 02-May-2019].

\bibitem{b2} A. M. Kuchling and E. S. Raymond, ``Curses Programming with Python,'' Curses Programming with Python - Python 3.7.3 documentation. [Online]. Available: \url{https://docs.python.org/3/howto/curses.html}. [Accessed: 02-May-2019].
\end{thebibliography}

>>>>

Go to \cite{b1} to see the complete source code for AILEE on Repl.it and play the game. It is recommended to play the game in a new tab for a better graphical experience.

@@

Before beginning the development of the game, a suitable platform to run the environment needed to be found. The website Repl.it was decided upon, due to their extensive language support and the ability for multiple people to work simultaneously and have all changes automatically saved to the cloud. \cite{b2} The “Multiplayer” mode, as this feature was called, still had a lot of bugs, so forking the project and saving work manually was still necessary, but overall it made the development of AILEE much smoother.

@@

To enable smooth graphics for the intro screen and the game’s ending events, the Python Curses library was referenced and used extensively. \cite{b3} This provided the ability to control keyboard input while text displayed on the screen or the ending event graphics played, to increase the smoothness of gameplay.

@@

Once the shell loads, the name of the computer exploited will be shown before the \texttt{/\$} symbol where commands are typed (Fig. \ref{fig:access}).

@@

Above is the code for the structure and mechanics of the computer filesystems.

@@

Directories are colored light blue, executables are light green, and regular files are white (Fig. \ref{fig:ls-command}). Unlike a real Linux terminal, the \textit{ls} command only works in the current directory and takes no arguments.

\section{Conclusion}
In summary, this project dives into many core concepts and facets of penetration testing, and simulates them to feel like the real-world counterparts. Many of the commands that simulate complicated software are coded creatively to look realistic even though they only work in the specific instances inside the game. AILEE is a demo, but there is much opportunity to expand the game into something far more complex and realistic if enough time and energy was dedicated to doing so.

\begin{thebibliography}{00}
\bibitem{b1} G. Haataja, D. Wilson, and M. Turnbull, “AILEE,” repl.it, 18-Apr-2019. [Online]. Available: \url{https://repl.it/@grantHaataja/AILEE}.

\bibitem{b2} Repl.it, ``The world's leading online coding platform,'' repl.it. [Online]. Available: \url{https://repl.it/site/features}. [Accessed: 02-May-2019].

\bibitem{b3} A. M. Kuchling and E. S. Raymond, ``Curses Programming with Python,'' Curses Programming with Python - Python 3.7.3 documentation. [Online]. Available: \url{https://docs.python.org/3/howto/curses.html}. [Accessed: 02-May-2019].

\end{thebibliography}
